|

### 2021-08-05 appendix/appendix.Rmd
added optimal mayor

>>>>

We need now to derive the optimal rents and public goods provision that the mayor proposes. The mayor benefits from public goods provision, as it increases the chances of her reelection. However, she also wants to receive some compensation XXXX

\[
\begin{aligned}
\max_{r, g} \quad & u(r) + B_M\pi(g)\\
\textrm{s.t.} \quad & r + g + C_g(N) \leq R
\end{aligned}
\]

And in equilibrium the budget binds, the optimal public goods provision maximizes:

\[
\max_{g} \{ u(R - g - C_g(N)) + B_M\pi(g) \}
\]

The first order condition for an optimal public goods provision makes the marginal benefits to increase rents, in this case, marginal costs of providing the public goods, equals to the marginal benefits of reelection:

\[
u'(R - g - C_g(N)) = B_M\pi'(g)
\]

This is sufficient for the equilibrium, as the second order condition reassures the concavity of the mayor's expected utility: $u''(R - g^* - C_g(N)) + B_M\pi''(g^*) < 0$.

\begin{proposition}
The provision of public goods increase with legislature size if the costs of govern decreases in larger legislatures.
\end{proposition}

\begin{proof}
In order to prove this result, we need to show that the mayor's expected utility satisfy the increasing differences in $g$ and $N$. This would mean that when increasing the size of the council, the optimal solution $g^*$ would also increase. However, as $N$ increases discretely, we cannot take a derivative on $N$ and use the implicit function theorem. We use Monotone Comparative Statics [@milgromshannonXXXX] to derive these results.

The mayor's expected utility
\end{proof}
